The Journey from Wild to Text Book Data: A Case Study of the National Longitudinal Survey of Youth

### 2021-05-05 report_alt.Rmd
Change the sequence of the plot in 3.2.1

Figure \ref{fig:comppict} A shows the mean hourly wage feature after the extreme values are replaced. It shows that the highest value has decreased to be around $350. The spikes were still observed but are not as extreme as the original data set. In Figure \ref{fig:comppict} B), we plotted the three features of mean hourly wages, namely the minimum, median, and maximum value, transformed to log scale. The plot implies that the skewness is slightly negative. We also see that the three features are overlapped each other. It indicates that some ID's minimum wages are higher than some ID's maximum wages.

@@

Furthermore, Figure \ref{fig:compare-plot} implies that the fluctuation can still be observed in the data after the treatment. However, the large spikes, which are considered "erroneous outliers", are already eliminated from the data. Hence, the model produces a data set with a more reasonable degree of fluctuation.

>>>>

Figure \ref{fig:compare-plot} shows the mean hourly wage before and after the extreme values are replaced. It implies that the fluctuation can still be observed in the data after the treatment. However, the large spikes, which are considered "erroneous outliers", are already eliminated from the data. Hence, the model produces a data set with a more reasonable degree of fluctuation.

Further, \ref{fig:comppict} A shows that after eliminating the extreme values, the highest value has decreased to be around $350. The spikes were still observed but are not as extreme as the original data set. In Figure \ref{fig:comppict} B), we plotted the three features of mean hourly wages, namely the minimum, median, and maximum value, transformed to log scale. The plot implies that the skewness is slightly negative. We also see that the three features are overlapped each other. It indicates that some ID's minimum wages are higher than some ID's maximum wages.

@@

### 2021-05-05 report_alt.tex
Change the sequence of the plot in 3.2.1

Figure \ref{fig:comppict} A shows the mean hourly wage feature after the extreme values are replaced. It shows that the highest value has decreased to be around \$350. The spikes were still observed but are not as extreme as the original data set. In Figure \ref{fig:comppict} B), we plotted the three features of mean hourly wages, namely the minimum, median, and maximum value, transformed to log scale. The plot implies that the skewness is slightly negative. We also see that the three features are overlapped each other. It indicates that some ID's minimum wages are higher than some ID's maximum wages.

@@

Furthermore, Figure \ref{fig:compare-plot} implies that the fluctuation can still be observed in the data after the treatment. However, the large spikes, which are considered ``erroneous outliers'', are already eliminated from the data. Hence, the model produces a data set with a more reasonable degree of fluctuation.

>>>>

Figure \ref{fig:compare-plot} shows the mean hourly wage before and after the extreme values are replaced. It implies that the fluctuation can still be observed in the data after the treatment. However, the large spikes, which are considered ``erroneous outliers'', are already eliminated from the data. Hence, the model produces a data set with a more reasonable degree of fluctuation.

Further, \ref{fig:comppict} A shows that after eliminating the extreme values, the highest value has decreased to be around \$350. The spikes were still observed but are not as extreme as the original data set. In Figure \ref{fig:comppict} B), we plotted the three features of mean hourly wages, namely the minimum, median, and maximum value, transformed to log scale. The plot implies that the skewness is slightly negative. We also see that the three features are overlapped each other. It indicates that some ID's minimum wages are higher than some ID's maximum wages.

@@
